### 2022-06-17 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@7018c2fbc6439ce51f68b1d0eeb77170b87fd7c8 🚀

%
Norma\,Forero Rocio Munoz%
%
\,\textsuperscript{1,2}\quad %
Renata L.\,Muylaert%
%
\,\textsuperscript{3}\quad %
Stephanie N.\,Seifert%
%
\,\textsuperscript{4}\quad %
Gregory F.\,Albery%
%
\,\textsuperscript{5}\quad %
Colin J.\,Carlson%
%
\,\textsuperscript{5}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}

\textsuperscript{1}\,Université de
Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
Sciences\quad \textsuperscript{3}\,Molecular Epidemiology and Public
Health Laboratory, Hopkirk Research Institute, Massey University,
Palmerston North, New Zealand\quad \textsuperscript{4}\,Paul G. Allen
School for Global Health, Washington State University, Pullman, WA,
United States\quad \textsuperscript{5}\,???

>>>>

%
Norma\,Forero Rocio Munoz%
%
\,\textsuperscript{1,2}\quad %
Renata L.\,Muylaert%
%
\,\textsuperscript{3}\quad %
Stephanie N.\,Seifert%
%
\,\textsuperscript{4}\quad %
Gregory F.\,Albery%
%
\,\textsuperscript{5}\quad %
Colin J.\,Carlson%
%
\,\textsuperscript{6,7,8}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}

\textsuperscript{1}\,Université de
Montréal\quad \textsuperscript{2}\,Québec Centre for Biodiversity
Sciences\quad \textsuperscript{3}\,Molecular Epidemiology and Public
Health Laboratory, School of Veterinary Science, Massey University, New
Zealand\quad \textsuperscript{4}\,Paul G. Allen School for Global
Health, Washington State University, Pullman, WA, United
States\quad \textsuperscript{5}\,Department of Biology, Georgetown
University, Washington, DC, USA\quad \textsuperscript{6}\,Department of
Biology, Georgetown University, Washington,
DC,\quad \textsuperscript{7}\,Center for Global Health Science and
Security, Georgetown University Medical Center, Washington, DC,
USA\quad \textsuperscript{8}\,Department of Microbiology and Immunology,
Georgetown University Medical Center, Washington, DC, USA

### 2022-06-17 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@7018c2fbc6439ce51f68b1d0eeb77170b87fd7c8 🚀

\medskip
\begin{flushleft}
{\small
%
Norma\,Forero Rocio Munoz%
%
\,\textsuperscript{1,2}, %
Renata L.\,Muylaert%
%
\,\textsuperscript{3}, %
Stephanie N.\,Seifert%
%
\,\textsuperscript{4}, %
Gregory F.\,Albery%
%
\,\textsuperscript{5}, %
Colin J.\,Carlson%
%
\,\textsuperscript{5}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}
\vskip 1em
\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences; \textsuperscript{3}\,Molecular
Epidemiology and Public Health Laboratory, Hopkirk Research Institute,
Massey University, Palmerston North, New
Zealand; \textsuperscript{4}\,Paul G. Allen School for Global Health,
Washington State University, Pullman, WA, United
States; \textsuperscript{5}\,???\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}

>>>>

\medskip
\begin{flushleft}
{\small
%
Norma\,Forero Rocio Munoz%
%
\,\textsuperscript{1,2}, %
Renata L.\,Muylaert%
%
\,\textsuperscript{3}, %
Stephanie N.\,Seifert%
%
\,\textsuperscript{4}, %
Gregory F.\,Albery%
%
\,\textsuperscript{5}, %
Colin J.\,Carlson%
%
\,\textsuperscript{6,7,8}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{1,2,‡}
\vskip 1em
\textsuperscript{1}\,Université de Montréal; \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences; \textsuperscript{3}\,Molecular
Epidemiology and Public Health Laboratory, School of Veterinary Science,
Massey University, New Zealand; \textsuperscript{4}\,Paul G. Allen
School for Global Health, Washington State University, Pullman, WA,
United States; \textsuperscript{5}\,Department of Biology, Georgetown
University, Washington, DC, USA; \textsuperscript{6}\,Department of
Biology, Georgetown University, Washington,
DC,; \textsuperscript{7}\,Center for Global Health Science and Security,
Georgetown University Medical Center, Washington, DC,
USA; \textsuperscript{8}\,Department of Microbiology and Immunology,
Georgetown University Medical Center, Washington, DC, USA\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Timothée Poisot --- \texttt{timothee.poisot@umontreal.ca}\\
}
\end{flushleft}
